SDR enhancement by clouds

### 2024-03-15 GHI_enh_04_investigate.tex
Commit 2024-03-15 20:14
Commit 2024-03-15 21:12

lmY: 8.781482 +/- 0.831715

{[}1{]} -17410.99
{[}1{]} 8.781482
(Intercept) dataset\$year
-17410.988738 8.781482

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

@@

@@

\begin{verbatim}
2024-03-15 17:07:40.1 athan@tyler GHI_enh_04_investigate.R 1.283610 mins
\end{verbatim}

>>>>

lmY: 341.6364 +/- 36.57038

@@

lmY: 122.2229 +/- 11.42113

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-2} \end{center}

lmY: 0.232986 +/- 0.055703

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-3} \end{center}

@@

\begin{verbatim}
2024-03-15 18:54:55.8 athan@tyler GHI_enh_04_investigate.R 1.392723 mins
\end{verbatim}

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 21:12

@@

@@

>>>>

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/P_energy-3.pdf")
```

@@

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/P_energy-2.pdf")
```

@@

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-1.png")
```

### 2024-03-15 article/article.tex
Commit 2024-03-15 21:12

@@

\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-13}
\end{figure}

>>>>

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-3}

\caption{Treds of the mean over irradiance per CE}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-3}
\end{figure}

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-2}

\caption{Trend of number of CE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-5}
\end{figure}

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-1}

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Distribution of the number of CE cases}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Distribution of CE above reference}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Distribution of CE groups}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-15}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-16}
\end{figure}
